Estimating individual subjective values of emotion regulation strategies

### 2023-02-14 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex

To investigate whether ER strategies reduce emotional arousal, we conducted an rmANOVA comparing the subjective arousal ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)).
Post-hoc test showed significantly reduced subjective arousal after use of distraction (\(\eta_{p}^{2}=0.05, [0.02, 1.00]\), \(BF_{10}=\)\(1.68 \times 10^{2}\)), distancing (\(\eta_{p}^{2}=0.03, [0.01, 1.00]\), \(BF_{10}=\)\(6.30 \times 10^{1}\)), and suppression (\(\eta_{p}^{2}=0.02, [0.00, 1.00]\), \(BF_{10}=\)\(1.97\)) compared with active viewing.
However, there were no significant differences between strategies (all \(p>.05\)).
To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVAS comparing \emph{Corrugator} activity and \emph{Levator} activity of four the strategies.
Regarding \emph{Corrugator} activity, we found a significant main effect of factor strategy (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)).
Post-hoc test revealed reduced \emph{Corrugator} activity during distraction (\(\eta_{p}^{2}=0.06, [0.03, 1.00]\), \(BF_{10}=\)\(2.19 \times 10^{4}\)), distancing (\(\eta_{p}^{2}=0.07, [0.03, 1.00]\), \(BF_{10}=\)\(1.40 \times 10^{5}\)), and suppression (\(\eta_{p}^{2}=0.08, [0.04, 1.00]\), \(BF_{10}=\)\(1.84 \times 10^{7}\)) compared to active viewing.
There were no significant differences between regulation strategies (all \(p>.05\)).

>>>>

To investigate whether ER strategies reduce emotional arousal, we conducted an rmANOVA comparing the subjective arousal ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)).
Post-hoc test showed significantly reduced subjective arousal after use of distraction (\(\eta_{p}^{2}=0.05, [0.02, 1.00]\), \(BF_{10}=\)\(1.68 \times 10^{2}\)), distancing (\(\eta_{p}^{2}=0.03, [0.01, 1.00]\), \(BF_{10}=\)\(6.30 \times 10^{1}\)), and suppression (\(\eta_{p}^{2}=0.02, [0.00, 1.00]\), \(BF_{10}=\)\(1.97\)) compared to active viewing.
However, there were no significant differences between strategies (all \(p>.05\)).
To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVA comparing \emph{Corrugator} activity and \emph{Levator} activity of four the strategies.
Regarding \emph{Corrugator} activity, we found a significant main effect of factor strategy (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)).
Post-hoc test revealed reduced \emph{Corrugator} activity during distraction (\(\eta_{p}^{2}=0.06, [0.03, 1.00]\), \(BF_{10}=\)\(2.19 \times 10^{4}\)), distancing (\(\eta_{p}^{2}=0.07, [0.03, 1.00]\), \(BF_{10}=\)\(1.40 \times 10^{5}\)), and suppression (\(\eta_{p}^{2}=0.08, [0.04, 1.00]\), \(BF_{10}=\)\(1.84 \times 10^{7}\)) compared to active viewing.
There were no significant differences between regulation strategies (all \(p>.05\)).

\hypertarget{subjective-effort-of-er-strategies}{%
\paragraph{Subjective effort of ER strategies}\label{subjective-effort-of-er-strategies}}

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\)).
Post-hoc test showed significant higher subjective effort for distraction (\(\eta_{p}^{2}=0.47, [0.42, 1.00]\), \(BF_{10}=\)\(3.61 \times 10^{30}\)), distancing (\(\eta_{p}^{2}=0.41, [0.35, 1.00]\), \(BF_{10}=\)\(1.60 \times 10^{28}\)), and suppression (\(\eta_{p}^{2}=0.30, [0.23, 1.00]\), \(BF_{10}=\)\(1.27 \times 10^{19}\)) compared to active viewing.
Moreover, we found significantly lower effort during suppression compared with distraction (\(\eta_{p}^{2}=0.08, [0.04, 1.00]\), \(BF_{10}=\)\(1.61 \times 10^{6}\)) and distancing (\(\eta_{p}^{2}=0.03, [0.01, 1.00]\), \(BF_{10}=\)\(2.92 \times 10^{1}\)).
